Priors

### 2023-06-20 reports/county_correlations.Rmd
update rmd files

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning=FALSE)

library(tidyverse)
library(targets)
library(here)
library(latex2exp)

@@

targets_dir <- here("_targets_6_19")

county <- tar_read(ma_v1, 
                   store =targets_dir) %>% 
  mutate(version = "v1") %>%
  bind_rows(
    tar_read(ma_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(ma_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(ma_v4, 
             store =targets_dir)
  # )%>%
  #  bind_rows(
  #   tar_read(ma_v5, 
  #            store =targets_dir)
  # )%>%
  #  bind_rows(
  #   tar_read(ma_v6, 
  #            store =targets_dir)
   )

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning=FALSE,cache=TRUE)

library(tidyverse)
library(targets)
library(here)
library(latex2exp)
library(kableExtra)

@@

targets_dir <- here("_targets")

county <- tar_read(ma_v1, 
                   store =targets_dir) %>% 
  mutate(version = "v1") %>%
  bind_rows(
    tar_read(ma_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(ma_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(ma_v4, 
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(ma_v5,
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(ma_v6,
             store =targets_dir)
   )

@@

```{r, fig.height=10, fig.width=12}

@@

cor_covid <- covidestim_correlations %>% 
  select(vlabel, 
         `Correlation with Covidestim Estimates`=Correlation)

cor_waste <- correlations %>% 
  select(vlabel, 
         `Correlation with Wastewater Concentrations`=Correlation)

cor_waste %>%
  left_join(cor_covid) %>%
  mutate(vlabel = gsub(
    "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$", 
    "Priors Do Not Vary by County and Date",
    vlabel, fixed=TRUE),vlabel=gsub(" at","\nat", vlabel)) %>%
  arrange(desc( `Correlation with Wastewater Concentrations`)) %>%
  rename(Implementation = vlabel) %>%
  kbl() %>%
  kable_styling(full_width = TRUE)

### 2023-06-20 reports/priors.Rmd
update rmd files

```{r beta-smoothing, fig.cap="The ratio of the screening test positivity over the overall test positivity from the COVID-19 Trends and Impact Survey is taken to be the estimate of $\\beta$. We compare two approaches to smoothing: cubic spline smoothing with 2 knots (July 15th, 2021 and December 1st, 2021) to LOESS smoothing with a span of 0.33."}

@@

```{r s-untested-smoothing, fig.cap="The percentage of the population experiencing COVID-19-like illness is taken to be the estimate of $\\Pr(S_1|\\text{untested}). The LOESS smoothed estimate with a span of 0.2 is shown in red."}

ctis_smoothed  %>%
  mutate(state=toupper(state)) %>%
  select(date,
         state, 
         contains("s_untested")) %>%
  pivot_longer(contains("s_untested")) %>%
  mutate(name = case_when(
    name == "s_untested_smoothed" ~ "LOESS smoothed",
    name == "imputed_s_untested" ~ "Survey Value"
  )) %>%
  ggplot(aes(x=date, y=value, color = name, 
             alpha = name, linewidth=name)) +
  geom_line() +
  facet_wrap(~state, ncol=5) +
  scale_alpha_manual(values=c("LOESS smoothed" = .9, 
                              "Survey Value"=.6),
                     name='') +
  scale_linewidth_manual(values = c("LOESS smoothed" = 1.02, 
                              "Survey Value"=.9)) +
  scale_color_manual(values=c("Survey Value" ="black", "LOESS smoothed"="darkred"),
                     name ='') +
  guides(alpha="none",
         linewidth="none",
         color = guide_legend(override.aes = list(
           linewidth = 3,
           alpha = c("LOESS smoothed" = .9, 
                     "Survey Value"=.3)),
                            nrow=3)) +
  theme_c(legend.position="top") +
  scale_x_date(date_breaks="3 months",
               date_labels = "%b %Y") + 
  labs(y = TeX("Survey Estimate of $Pr(S_1|untested)$"),
       x= "",
       title = TeX("Comparing Approaches for Smoothing Survey Estimates of $Pr(S_1|untested)$"))

>>>>

```{r beta-smoothing, fig.cap="The ratio of the screening test positivity over the overall test positivity from the COVID-19 Trends and Impact Survey is taken to be the estimate of $\\beta$. We compare two approaches to smoothing: cubic spline smoothing with 2 knots (July 15th, 2021 and December 1st, 2021) to LOESS smoothing with a span of 0.33.", fig.width=12,fig.height=12}

@@

```{r s-untested-smoothing, fig.cap="The percentage of the population experiencing COVID-19-like illness is taken to be the estimate of $\\Pr(S_1|\\text{untested}). The LOESS smoothed estimate with a span of 0.2 is shown in red.",fig.width=12,fig.height=16}

ctis_smoothed  %>%
  mutate(state=toupper(state)) %>%
  select(date,
         state, 
         contains("s_untested")) %>%
  pivot_longer(contains("s_untested")) %>%
  mutate(name = case_when(
    name == "s_untested_smoothed" ~ "LOESS smoothed",
    name == "imputed_s_untested" ~ "Survey Value"
  )) %>%
  ggplot(aes(x=date, y=value, color = name, 
             alpha = name, linewidth=name)) +
  geom_line() +
  facet_wrap(~state, ncol=4) +
  scale_alpha_manual(values=c("LOESS smoothed" = .9, 
                              "Survey Value"=.6),
                     name='') +
  scale_linewidth_manual(values = c("LOESS smoothed" = 1.02, 
                              "Survey Value"=.9)) +
  scale_color_manual(values=c("Survey Value" ="black", "LOESS smoothed"="darkred"),
                     name ='') +
  guides(alpha="none",
         linewidth="none",
         color = guide_legend(override.aes = list(
           linewidth = 3,
           alpha = c("LOESS smoothed" = .9, 
                     "Survey Value"=.3)),
                            nrow=3)) +
  theme_c(legend.position="top") +
  scale_x_date(date_breaks="3 months",
               date_labels = "%b %Y") + 
  labs(y = TeX("Survey Estimate of $Pr(S_1|untested)$"),
       x= "",
       title = TeX("Comparing Approaches for Smoothing Survey Estimates of $Pr(S_1|untested)$"))
